Response to the defense feedback

### 2021-06-01 changelog.tex
Updates from Overleaf

b. Quincunx defines the amount of leaked information by the empirical entropy of the observations. For a determinism program, channel capacity is the tight upper bound of the the empirical entropy of the observation. That's why I used the term ``lower bound'' during my PhD defense. I have removed the term ``lower bound'' to avoid any confusion in my dissertation.

@@

a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''.

>>>>

b. Quincunx defines the amount of leaked information by the empirical entropy of the observations. For a determinism program, channel capacity is the tight upper bound of the empirical entropy of the observation. In the early draft of the paper, I use the term ``conservative''. Dr. Wu thinks ``conservative'' might be a confusing term and suggests me with the term ``lower bound''. That's the reason that I used the term ``lower bound'' during my PhD defense. I have removed the term ``lower bound'' to avoid any confusion in my dissertation.

@@

a. I revised the description in Chapter 5. I avoided the use of term ``lower bound'' and tune my presentation.
